---
title: "macroinvertebrate_processing_2021_in-house-processed"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "2/3/2021"
output: html_document
params:
  file_name: "L:/DOW/BWAM Share/data/lab_data/WAA/2023/raw/MacroTaxa_470.23.csv"
  user: kareynol
  file_type: "waa"
---

```{r include=FALSE,message=FALSE}
library(skimr)
library(arrow)
library(dplyr)
library(readr)

#file_type options : "waa" or "internal"

#run the functions script - this is a set of functions i wrote for prepping the macro data
source("functions.R")

```

```{r}

#11/5/2024 reading in everything in the L drive for 2023 and 2024 - which is just DEER river for 2024 and we are still missing 2023 lake data of of 12/4/024
#so this skips the parameter above for the file, but that's ok. 
list<-list.files("L:/DOW/BWAM Share/data/lab_data/WAA/2023/raw/",
                 pattern = "*.csv",
                 full.names = TRUE)
raw.file<-lapply(list,
                 read.csv)

#merge them together
raw<-bind_rows(raw.file,
               .id = "column_label")

raw<-raw %>% 
  mutate(MSSIH_EVENT_SMAS_HISTORY_ID = case_match(
    MSSIH_EVENT_SMAS_HISTORY_ID,
    "Archer Creek"~"11-ARCH-1.9", #archer creek is also missing the method, fixing now for a standard kick - this one is not actually RMN - maybe we should rename the project.
    .default = MSSIH_EVENT_SMAS_HISTORY_ID
  )) %>% 
  mutate(MSSIH_BIOSAMPLE_COLLECT_METHOD = case_when(
    Client_Project_Name %in% "RMN"~"Kick: Standard",
    TRUE ~MSSIH_BIOSAMPLE_COLLECT_METHOD))

if(params$file_type=="internal"){m_data_prep(raw)}

if(params$file_type=="waa"){waa_data_prep(raw) #this funtion cleans up the file and gets it ready to be injested into the BAP script
 prepped_df<-prepped_df3 #renames and copies the df that was made 
}


#11/4/24 check to see why there are less records - Archer creek is teh missing records - these are not ours
sites.raw<-unique(raw$MSSIH_EVENT_SMAS_HISTORY_ID)
sites.merged<-unique(prepped_df3$MSSIH_EVENT_SMAS_HISTORY_ID)

setdiff(sites.raw,sites.merged) # Yes confirmed it is Archer Creek, which was renamed WAA provides us this data and i'm not sure why; fixed no remaining differences



```

```{r}
#prep for tables for Data Mod: this will do the macro species sample event table and the 
#Sample info history tables, and save it to the outputs folder with today's date. Hashed out for this review

if (params$file_type=="internal"){tables_1_2(prepped_df)}
if (params$file_type=="waa"){tables_1_2.waa(prepped_df)}

```

```{r}
#Run BAP and create BAP entry for table
library(BAP)

#run BAP's data prep on the raw file
bap.prepped<-BAP::data_prep(prepped_df)
#2022 data fixes, references seemed odd
bap.prepped$REFERENCE<-""
bap.prepped<-bap.prepped %>% 
  distinct()

#split by collection method and run the appropriate BA
bap.final<-apply_bap(bap.prepped)

#this is probably where we can figure out the new code from - start here

#create metric file with correct names
metrics_final<-metric_table(bap.final)

sites.event<-unique(samp_event$MSSIH_EVENT_SMAS_HISTORY_ID)
sites.metrics<-unique(metrics.subset$site_id)

setdiff(sites.event,sites.metrics) #these are all low gradient besides the lake 04-LHONYE-0.0, so will not be in the metrics file anyway
# "04-LHONYE-0.0" "10-DUTT-0.6"   "10-RILE-0.5"   "10-WOOD-3.8"   "12-NMIL-0.5"   "17-WILT-0.7"  these are the guys
```
Prep for WQMA

```{r WQMA-data-integration}

#write these to the L drive, hashed out to not overwrite
#write.csv(metrics.subset, "L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/METRICS_2023_processed_11_5_24_KAR.csv" )
#write.csv(samp_event,"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/MACRO_SAMP_INF_2023_processed_11_5_24_KAR.csv")

#combine deer river and 2023 samples and re-save
event_2023<-read.csv("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/MACRO_SAMP_INF_2023_processed_11_5_24_KAR.csv")
event_deer<-read.csv("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/20241007_S_MACRO_SAMP_INF_HIST_deer_river.csv")
#add missing group column (not used for streams)
event_deer$MSSIH_GROUP<-""

#bind them
final_event<-rbind(event_2023,event_deer) #good they match
final_event$X<-NULL #remove weird column

#write to folder and move the archive that was the originals to another folder (archive)
#write.csv(final_event,"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/2023_all_2024_deer_river_sample_inf.csv")
#i saved these to file just in cae


#read in th two metric files
metrics_2023<-read.csv("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/METRICS_2023_processed_11_5_24_KAR.csv")
metrics_deer<-read.csv("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/archive/20241007_METRICS_deer_river.csv")

#bind them, these have differing columns bc of hte metric differences; but the amount is fine - 377 of 2023 plus 6 from deer river for 383 total - which is less than the event table since some of them CANT have metrics calculated yet.
final_metrics<-dplyr::full_join(metrics_2023,metrics_deer)

#join a couple fields to the metrics file 
cols<-final_event %>% 
  select(MSSIH_BIOSAMPLE_COLLECT_METHOD,
         MSSIH_BIOSAMPLE_COLLECT_METHOD_NUM,
         MSSIH_EVENT_SMAS_HISTORY_ID,
         MSSIH_EVENT_SMAS_SAMPLE_DATE,
         MSSIH_REPLICATE,
         MSSIH_GROUP,
         MSSIH_LINKED_ID_VALIDATOR) #403 in the original event table, this accounts for the low gradient and the one lake one for 2023 data

setdiff(final_event$MSSIH_EVENT_SMAS_HISTORY_ID,final_metrics$site_id)#403 in the original event table, this accounts for the low gradient and the one lake one for 2023 data
# "04-LHONYE-0.0" "10-DUTT-0.6"   "10-RILE-0.5"   "10-WOOD-3.8"   "12-NMIL-0.5"   "17-WILT-0.7"  these are the guys
#rename missing column for join
final_metrics$MSSIH_LINKED_ID_VALIDATOR<-final_metrics$MMDH_LINKED_ID_VALIDATOR

final_metrics_2<-left_join(final_metrics,cols,
                           by = "MSSIH_LINKED_ID_VALIDATOR")
if (nrow(final_metrics_2) != nrow(cols)) {stop("Number of rows don't match, check the matching - it could be low gradient samples or lakes with no metrics")}
#it didnt this is because of the low gradient as noted above

final_metrics_2$EVENT_ID<-NULL #remove the event id as it's not in the right format - it's the output from the BAP package

#write to folder and move the archive that was the originals to another folder (archive)
#write.csv(final_metrics_2,"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/2023_all_2024_deer_river_metrics.csv")
```

Site corrections from the look-up file from Charlie

```{r site-id-corrections}

#read in the 2023 ones
sites_survey_23<-readxl::read_excel("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/siteIdCrosswalkTable2023_v1.xlsx")
sites_survey_24<-readxl::read_excel("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/siteIdCrosswalkTable2024_v3.xlsx")


sites_23<-sites_survey_23 %>% 
  select(SITE_CODE,ORIGINAL_SITE_CODE, SEIH_EVENT_SMAS_SAMPLE_DATE,SEIH_SMAS_ARRIVETIME,eventSMASId) %>% 
  mutate(EVENT_ID = eventSMASId,
         DATE = SEIH_EVENT_SMAS_SAMPLE_DATE) %>% 
  mutate(DATE = as.Date(DATE, "%m/%d/%y")) %>% 
  distinct() %>% 
  select(c(SITE_CODE,ORIGINAL_SITE_CODE,EVENT_ID,DATE))

sites_24<-sites_survey_24 %>% 
    select(finalSiteID,revisedOriginalSiteID, eventSMASSampleDate,eventSMASArrivetime,eventSMASId_2) %>% 
  mutate(EVENT_ID = eventSMASId_2,
         DATE = eventSMASSampleDate) %>% 
  mutate(DATE = as.Date(DATE, "%m/%d/%Y")) %>% 
  rename(ORIGINAL_SITE_CODE = revisedOriginalSiteID,
         SITE_CODE = finalSiteID) %>% 
  distinct() %>% 
  select(c(SITE_CODE,ORIGINAL_SITE_CODE,EVENT_ID,DATE))

#combine 23 and 24
sites_23_24<-rbind(sites_23,
                   sites_24) %>% 
  rename(site_id = ORIGINAL_SITE_CODE,
         final_id = SITE_CODE)# number of rows match here for the rbind
sites_23_24<-sites_23_24 %>% 
  distinct()

#ok now we'll bind to the final_metrics_2 df before we adjust for WQMA compatability

final_metrics_2$DATE<-as.Date(final_metrics_2$DATE,"%Y-%m-%d")

final_metrics_3<-left_join(
  final_metrics_2,
  sites_23_24,
  by = c("site_id","DATE")
)

#let's look at the ones that didnt join
missing_events<-final_metrics_3 %>% 
  subset(is.na(final_id))


#site adjustments based on the join - there will likely be some here that do not exist and need to be created

final_metrics_4<-final_metrics_3 %>% #first correct dates that don't match the surveys
  mutate(site_id = case_when(site_id %in% '11-LHUD-117.1'~'13-LHUD-117.1',
                             TRUE ~ site_id),
         new_DATE =
           case_when(site_id %in% '10-BOQT-28.6' & DATE == "2023-07-27"~"2023-07-26",
                     site_id %in% "10-GRAV-5.7" & DATE %in% "2023-07-27"~"2023-07-25",
                     site_id %in% '10-LSAB-17.6' & DATE %in% "2023-07-26"~"2023-07-25",
                     site_id %in% '10-LSAB-5.7' & DATE %in% "2023-07-26"~"2023-07-25",
                     #site_id %in% '10-SABL_W-32.1' & DATE %in% "2023-07-20"~"2023-07-26",
                     site_id %in% '10-SARA-21.8' & DATE %in% "2023-07-26"~"2023-07-25",
                     site_id %in% '11-UHUD-2.0' & DATE %in% "2023-09-01"~"2023-09-13",
                     site_id %in% '12-MOHK-65.8' & DATE %in% "2023-09-01"~"2023-09-12",
                     site_id %in% '12-MOHK-65.8' & DATE %in% "2023-09-14"~"2023-09-12",
                     site_id %in% '13-LHUD-117.1' & DATE %in% "2023-09-17"~"2023-09-11",
                     TRUE ~ paste(DATE)

           )) %>%
  mutate(DATE = as.Date(new_DATE,"%Y-%m-%d"))


#check for missing sites again - first remove the old joined columns since they will re-join and mess it up
final_metrics_4<-final_metrics_4 %>% 
  select(-c(final_id,EVENT_ID))

final_metrics_4<-left_join(
  final_metrics_4,
  sites_23_24,
  by = c("site_id","DATE")
)

#let's look at the ones that didnt join
missing_events<-final_metrics_4 %>% 
  subset(is.na(final_id))

#make notes for these
missing_events<-missing_events %>% 
  mutate(notes = "",
         missing_survey = "",
         missing_site = "") %>% 
  mutate(missing_site = case_when(
    site_id %in% "10-CADE-6.2"~"T",
    site_id %in% "10-SABL_W-25.6" ~"F",
    site_id %in% "10-SMOW-0.1" ~"T", 
    site_id %in% "11-ARCH-1.9" ~"F", 
    site_id %in% "11-BORE-13.6" ~"T", 
    site_id %in% "11-BORE-19.4" ~"T",
    site_id %in% "11-GULF-0.7" ~"T",
    site_id %in% "11-JONS-2.1" ~"T",
    site_id %in% "11-WPBR-0.6" ~"T",
    site_id %in% "12-SIMB-0.5" ~"T",
    site_id %in% "13-LHUD-117.1" ~"T",
    site_id %in% "11-UHUD-42.5" ~ "F",
    TRUE~"F")) %>% 
  mutate(missing_survey = case_when(
      site_id %in% "10-CADE-6.2"~"T",
    site_id %in% "10-SABL_W-25.6" ~"T",
    site_id %in% "10-SMOW-0.1" ~"T", 
    site_id %in% "11-ARCH-1.9" ~"T", 
    site_id %in% "11-BORE-13.6" ~"T", 
    site_id %in% "11-BORE-19.4" ~"T",
    site_id %in% "11-GULF-0.7" ~"T",
    site_id %in% "11-JONS-2.1" ~"T",
    site_id %in% "11-WPBR-0.6" ~"T",
    site_id %in% "12-SIMB-0.5" ~"T",
    site_id %in% "11-UHUD-42.5" ~ "T",
    
    TRUE~"F"
  )) %>% 
    mutate(notes = case_when(
    site_id %in% "10-CADE-6.2"~"Not in site selection template either",
    site_id %in% "10-SABL_W-25.6" ~"There are 3 potential matches in the survey, 7/26/23 matched fine, but there is another date 7/20 with 2 replicates??",
    site_id %in% "10-SMOW-0.1" ~"This one is not in teh sites table or the 23 site selection, maybe Tom? ", 
    site_id %in% "11-ARCH-1.9" ~"Create event id", 
    site_id %in% "11-BORE-13.6" ~"Not in sites table or 23 site selection", 
    site_id %in% "11-BORE-19.4" ~"Not in sites table or 23 site selection",
    site_id %in% "11-GULF-0.7" ~"Not in sites table or 23 site selection",
    site_id %in% "11-JONS-2.1" ~"Not in sites table or 23 site selection",
    site_id %in% "11-WPBR-0.6" ~"Not in sites table or 23 site selection",
    site_id %in% "12-SIMB-0.5" ~"Not in sites table or 23 site selection",
    site_id %in% "11-UHUD-42.5" ~ "no matching dates for this site",
    TRUE~"F"))

#checked - these do not exist in the existing survey checks OR the 2023 that are in the database
#write to .csv for checking, then hashed out to keep from overwriting when checking
#write.csv(missing_events,here::here("outputs/bap_missing_sites_surveys_12_5_24.csv"))

#create the one event ID that I can - the one that has a site that exists already -11-ARCH-1.9

final_metrics_4<-final_metrics_4 %>% 
  mutate(EVENT_ID = case_when(
    site_id %in% "11-ARCH-1.9"~"11-ARCH-1.9_20230918T1200",
    site_id %in% "10-CHUB-2.2" ~ "10-CHUB-2.2_20230726T1200",
    site_id %in% "10-SABL-0.4"~ "10-SABL_E-0.4_20230726T1230",
    site_id %in% "13-WAPP_E-3.2" ~ "13-WAPP_E-3.2_20240718T1038",
    site_id %in% "10-JACK-0.2" ~ "10-JKBR-0.2_20230726T1030",
    TRUE ~ EVENT_ID
  ),
  final_id = case_when(
    site_id %in% "10-SABL-0.4" ~ "10-SABL_E-0.4",
    site_id %in% "11-ARCH-1.9" ~ "11-ARCH-1.9",
    site_id %in% "10-JACK-0.2" ~ "10-JKBR-0.2",
    site_id %in% "13-WAPP_E-3.2" ~ "13-WAPP_E-3.2",
    TRUE ~ final_id))

#subset to the complete ones for creating the .RDS files
final_metrics_5<-final_metrics_4 %>% 
  filter(!is.na(EVENT_ID)) 

#clean it up
final_metrics_5<-final_metrics_5 %>% 
  mutate(MSSIH_EVENT_SMAS_HISTORY_ID = final_id,
         MSSIH_EVENT_SMAS_SAMPLE_DATE = DATE) %>% #make all the columns agree
  select(-c(new_DATE,date)) %>% 
  distinct()

#write to file
# write.csv(final_metrics_5,"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/2023_all_2024_deer_river_metrics_cleaned_preWQMAval.csv")



```

```{r create-new-sample-final}
#create new sample file as well

sample_final<-final_metrics_5 %>% 
  select(c(starts_with("MSSIH_"),EVENT_ID))

#need the counts-so we'll get those from the originally created sample table
samp_small<-final_event %>% 
  select(c(MSSIH_LINKED_ID_VALIDATOR, #we cna use the originally created linked validator to join
           MSSIH_TAXONOMIST,
           MSSIH_TOTAL_INDIV_CNT,
           MSSIH_TOTAL_INDIV_CNT_NOTE)) %>% 
  distinct()
  
sample_final_2<-left_join(sample_final,samp_small,
                          by = "MSSIH_LINKED_ID_VALIDATOR") #total rows match the original

sample_final_2<-sample_final_2 %>% 
  distinct()
#create check
final_metrics_5<-final_metrics_5 %>% 
  distinct()

if (nrow(sample_final_2) != nrow(final_metrics_5)) {stop("Number of rows don't match, check the matching")}

#save to file
 #write.csv(sample_final_2,"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores/2023_all_2024_deer_river_sample_inf_cleaned_preWQMAval.csv")
```


Convert data to new format using Zach's code
https://github.com/BWAM/data_warehouse_prep/blob/main/R/s_macro_metrics.R


Prep the macro sample file for the WQMA database

```{r grab-event-table}

#check to see if the sites are already in there
obt_result_dir <- file.path(
  "L:",
  "DOW",
  "BWAM Share",
  "data",
  "parquet",
  "analytical_table_store",
  "obt_result.parquet"
)

#collect unique stream sites/dates

stream_df <- open_dataset(obt_result_dir) |> 
  filter(WATERBODY_TYPE %in% "river_stream") |>
  distinct(WATERBODY_TYPE, SITE_CODE) |>
  collect()

streams_sites<-unique(stream_df$SITE_CODE)

missing_sites<-setdiff(sites.metrics,streams_sites)
#i think now this part is unecessary since i matched using the surveys above. The surveys will be what Charlie is using to create new sites so that should be all of them. I subsetted the missing events (surveys) into an output folder that we'll work through.

```

This is more functions from the WQMA workup from Zach, i'll leave them in for now, and we can update as needed

```{r}
correct_site_name <- function(df, vars) {
  final_df <- df |>
    dplyr::mutate(
      dplyr::across(
        {{vars}},
        site_corrections
      ),
      .before = everything()
    )
}

site_corrections <- function(col) {
  stringr::str_replace_all(
    col,
    c("12-SAUQ-2.2" = "12-SAUQ-1.7",
      "13-LHUD-105" = "13-LHUD-105.0",
      "14-LBEV-0.1" = "14-LBEV_T03-0.1",
      "14-LBEV-0.4" = "14-LBEV_T01-0.4",
      "14-LBEV-0.3" = "14-LBEV_T04-0.3",
      "11-TWNS-0.2" = "11-STEB-0.2",
      "11-TWNS-1.1" = "11-STEB-1.1",
      "06-BIBS-0.3" = "06-JENC-0.3",
      "06-BIBS-6.6" = "06-JENC-6.6",
      "12-BATV-11.5" = "12-MITB-0.1",
      "13-BVRD-0.8" = "13-SHIR-0.8",
      "13-BVRD-1.0" = "13-SHIR-1.0",
      "13-BVRD-2.8" = "13-SHIR-2.8",
      "13-BVRD-4.8" = "13-SHIR-4.8",
      "05-CAMP- 1.5" = "05-CAMB-1.5",
      "06-FABS-5.0" = "06-TOLF-1.8",
      "12-SCHE-0.6" = "12-BRWC-0.6",
      "12-SCHE-0.8" = "12-COWC-0.8",
      "05-SEEL-0.5" = "05-MLIC-0.5",
      "11-SNOK-0.3" = "11-SNOK_L-0.3",
      "13-TACK-0.1" = "13-SPAR_T10-0.1",
      "06-CATH_T9_3a-0.5" = "05-CATH_T9_3a-0.5",
      "07-SKAT_1-0.2" = "07-SKAT_T89-0.2",
      "07-CAYG_2-1.1" = "07-CAYG-1.1",
      "07-BSWP_1.3" = "07-BSWP-1.3",
      "13-LINK-2.3" = "15-LINK-2.3",
      "07-GROU_1-1.5" = "07-GROU-1.5",
      "04-BAKE-0.3" = "04-BKER-0.3",
      "07-BLKC-2.8" = "11-BLKC-2.8",
      "07-BLCK-2.8" = "11-BLKC-2.8",
      "07-BUTN-0.6" = "07-BTNC-0.6",
      "14-COLE-0.4" = "14-CCLV-0.4",
      "05-CRAN-0.1" = "05-CRBP-0.1",
      "07-DEAN-1.9" = "07-DNCR-1.9",
      "07-FISC-1.3" = "07-FSHR-1.3",
      "10-JACK-0.2" = "10-JKBR-0.2",
      "08-LIME-6.7" = "08-LMKN-6.7",
      "13-SILV-4.5" = "13-SILS-4.5",
      "04-COHO_T41-0.1" = "05-COHO_T41-0.1",
      "07-SPRN_T7-0.1" = "04-SPRN_T7-0.1",
      "07-SENP_T32-0.6" = "04-SENP_T32-0.6",
      "07-MUDG_T72-0.3" = "04-MUDG_T72-0.3",
      "12-DWAS-7.2" = "11-DWAS-7.2",
      "04-GRIM-6.3" = "07-GRIM-6.3",
      "02-JNSN-2.3" = "03-JNSN-2.3",
      "02-MUDC-0.4" = "03-MUDC-0.4",
      "04-TNCR-3.7" = "05-TNCR-3.7",
      "03-WCAN-73.0" = "04-WCAN-73.0",
      "95-COHO-28.6" = "05-COHO-28.6",
      "04-SXML-2.2" = "07-SXML-2.2",
      "12-HVLY-0.5" = "12-HLVY-0.5",
      "11-UHUD-42.5" = "11-UHUD-43.1",
      "12-MOHK-3.7" = "12-MOHK-1.5",
      "05-CHAU-14.9" = "01-CHAU-14.9",
      "05-TOGA-1.5" = "05-TOGA-1.3",
      "13-SPAR_T96-01" = "13-SPAR_T9b-0.1",
      "13-TINW-4.55" = "13-TINW-4.5",
      "13TINW-4.5" = "13-TINW-4.5",
      "13TINW-6.5" = "13-TINW-6.5",
      "15-DEFT_T1-0.5" = "15-DEFT_T1-0.1",
      "15-DEFT_T1-0.2" = "15-DEFT_T1-0.1",
      "13-STNY-8.1" = "13-STNY-10.0",
      "14-GOUL-0.9" = "14-COUL-0.9",
      "12-NORT-1.7" = "12-NORT-2.3",
      "05-CHAU-4.2" = "05-CHAU-4.0",
      "02-CLER_T6-3.1" = "02-TWTY-3.1",
      "12-STLE-0.8" = "12-STLE-0.2",
      "13-BRNX-5.6" = "17-BRNX-5.6",
      "11-LRNC_21-20.2" = "11-UHUD-64.4",
      "11-UHUD-14.7" = "11-UHUD-14.8",
      "11-UHUD-27.5" = "11-UHUD-27.4",
      "11-UHUD-32.1" = "11-UHUD-32.4",
      "11-UHUD-39.5" = "11-UHUD-40.1",
      "11-UHUD-39.8" = "11-UHUD-40.3",
      "11-UHUD-42.5" = "11-UHUD-43.1",
      "11-UHUD-51.0" = "11-UHUD-51.3",
      "11-UHUD-64.0" = "11-UHUD-64.2",
      "11-UHUD-98.3" = "11-UHUD-98.7",
      "11-UHUD-267.8" = "11-UHUD-106.3",
      "11-UHUD-273.0" = "11-UHUD-111.6",
      "11-UHUD-284.9" = "11-UHUD-124.2",
      "11-UHUD-286.0" = "11-UHUD-124.7",
      "11-XHR-273.0" = "11-UHUD-111.6",
      "11-XHR-277.0" = "11-UHUD-115.6",
      "11-XHR-282.3" = "11-UHUD-120.9",
      "11-XHR-285.0" = "11-UHUD-124.3",
      "11-XHR-286.6" = "11-UHUD-125.3",
      "13-LHUD-25.8" = "13-LHUD-5.7",
      "13-LHUD-35.0" = "13-LHUD-14.7",
      "13-LHUD-39.7" = "13-LHUD-19.5",
      "13-LHUD-50.3" = "13-LHUD-47.5",
      "13-LHUD-50.59" = "13-LHUD-47.8",
      "13-LHUD-50.6" = "13-LHUD-47.9",
      "13-LHUD-50.61" = "13-LHUD-47.9",
      "13-LHUD-66.3" = "13-LHUD-63.6",
      "13-LHUD-67.3" = "13-LHUD-64.6",
      "13-LHUD-89.3" = "13-LHUD-88.7",
      "13-LHUD-104.6" = "13-LHUD-105",
      "13-LHUD-119.6" = "13-LHUD-124.9",
      "13-LHUD-120.2" = "13-LHUD-125.5",
      "13-LHUD-124.1" = "13-LHUD-128.9",
      "13-LHUD-125.8" = "13-LHUD-130.6",
      "13-LHUD-133.4" = "13-LHUD-140.1",
      "13-LRNC_22-89.3" = "13-LHUD-88.6",
      "13-LRNC_63-133.4" = "13-LHUD-140.1",
      "13-LRNC_66-119.6" = "13-LHUD-124.9",
      "03-YANT_T1C-0.2" = "03-YANT_T1c-0.2",
      "17-GSCK_TA-0.1" = "17-GSCK_Ta-0.1",
      "07-SKAT_T93A-0.5" = "07-SKAT_T93a-0.5",
      "06-SANG_TB-0.1" = "06-SANG_Tb-0.1",
      "05-CATH_T9_3A-0.5" = "05-CATH_T9_3a-0.5",
      "07-SKAT_T93A-0.5" = "07-SKAT_T93a-0.5",
      "14-CALL_E_T13A-0.1" = "14-CALL_E_T13a-0.1",
      "09-STLW_T46A-0.1" = "09-STLW_T46a-0.1",
      "07-SKAT_T93A-0.5" = "07-SKAT_T93a-0.5",
      "12-SCHO_T93_B-1.8" = "12-SCHO_T93_b-1.8",
      "13-SPAR_T9B-0.1" = "13-SPAR_T9b-0.1",
      "17-BLND_TB-2.0" = "17-BLND_Tb-2.0",
      "17-KENF_TA-0.2" = "17-KENF_Ta-0.2",
      "07-KDIG_TB-0.7" =  "07-KDIG_Tb-0.7",
      "17-KENF_TA-0.2" = "17-KENF_Ta-0.2",
      "17-BLND_TB-2.0" = "17-BLND_Tb-2.0",
      "17-KENF_TA-0.2" = "17-KENF_Ta-0.2",
      "17-BLND_TB-2.0" = "17-BLND_Tb-2.0",
      "13-SPAR_T9B-0.1" = "13-SPAR_T9b-0.1",
      "02-WRGT_TA-1.8" = "02-WRGT_Ta-1.8",
      "13-LHUD-47.91" = "13-LHUD-47.9",
      "05-MILD_T7-0.3" = "04-MILD_T7-0.3"
      # "11-UHUD-43.1",
      # "13-PATS-0.5",
      # "13-PATS-1.3",
      # "13-PATS-1.8",
      # "12-SAUQ-1.7",
      # "12-POEN-2.0",
    )
  )
}

macro_event_corrections <- function(df) {
  mutate(
    df,
    event_id = case_match(
      event_id,
      "12-MOYR-5.1_20100729" ~ "12-MOYR-5.1_20100728",
      "12-OTSO -1.1_20200714" ~ "12-OTSO-1.1_20200714",
      "01-LBUF-2.5_20200917" ~ "01-LBUF-2.5_20200915",
      "02-WFREN_T12-0.2_20210915" ~ "02-WFREN_T12-0.5_20210915",
      "1-BUFF-1.7_20200902" ~ "1-BUFF-1.7_20200901",
      "01-BUFF-1.7_20200902" ~ "01-BUFF-1.7_20200901",
      "11-WBLA-0.9_20210803" ~ "11-WBLA-0.9_20210805",
      "04-UGNS-139.6_20220929" ~ "04-UGNS-139.6_20220921",
      "05-COHO_T1-0.1_20220830" ~ "05-COHO_T1-0.1_20220831",
      "05-FIVM-13.0_20220830" ~ "05-FIVM-13.0_20220831",
      "05-STEO_T22-0.2_20220830" ~ "05-STEO_T22-0.2_20220831",
      "06-SUSQ-36.9_20220713" ~ "06-SUSQ-36.9_20220712",
      "08-FALK-0.3_20220914" ~ "08-FALK-0.3_20220915",
      "08-MILE-0.7_20220914" ~ "08-MILE-0.7_20220915",
      "08-TANE-0.7_20220913" ~ "08-TANE-0.7_20220914",
      "13-SPAR-3.6_20220714" ~ "13-SPAR-3.6_20220719",
      "12-SPIT-2.3_20210723" ~ "12-SPIT-2.3_20200723",
      "12-WESK-0.1_20200716" ~ "12-WESK_T5-0.1_20200716",
      "07-CANO-2.3_20210721" ~ "07-CANO-0.8_20210721",
      "07-DEAN-0.1_20210721" ~ "07-DEAN-1.9_20210721",
      "13-ESOP-4.4_20220720" ~ "13-ESOP-4.8_20220720",
      # "13-POST-0.8_20220719" ~ "13-POST-18.4_20220719",
      # "13-ROND-9.2_20220719" ~ "13-ROND-32.2_20220719",
      "13-TIOR-0.2_20220720" ~ "13-TIOR-0.1_20220720",
      "07-FISC-0.1_20210722" ~ "07-FISC-1.3_20210722",
      "07-POTT-0.7_20210831" ~ "07-POTT-0.1_20210831",
      "07-RHCR-0.8_20210713" ~ "07-RHCR-0.7_20210713",
      "07-RHCR-0.8_20210901" ~ "07-RHCR-0.7_20210901",
      "11-UHUD-125.3_20210803" ~ "11-UHUD-124.7_20210803",
      "01-CHAU-4.2_20220922" ~ "01-CHAU-4.0_20220922",
      "05-CDEA-11.4_20220831" ~ "05-CDEA-11.5_20220831",
      "05-CHEM-33.8_20220830" ~ "05-CHEM-33.6_20220830",
      "05-COHO-1.4_20220830" ~ "05-COHO-1.5_20220830",
      "05-PURD-0.1_20220831" ~ "05-PURD-0.2_20220831",
      # "05-TRPS-9.5_20220901" ~ "05-TRPS-7.0_20220901",
      "08-BLCK-30.0_20220802" ~ "08-BLCK-30.4_20220802",
      "08-LIME-6.3_20220914" ~ "08-LIME-6.7_20220914",
      "08-WHET-4.8_20220914" ~ "08-WHET-4.9_20220914",
      "11-XHR-296.0_20210803" ~ "11-UHUD-296.7_20210803",
      "05-MDCR-10.0_20220821" ~ "05-MDCR-10.0_20220831",
      "05-MEAD-10.8_20220831" ~ "05-MEAD-10.9_20220830",
      "07-VENS-1.8_20210722" ~ "07-VENE-1.5_20210722",
      "03-LSTN-1.0_20200801" ~ "03-LSTN-1.0_20200819",
      "08-ADKS_36-0.5_20220914" ~ "08-ADKS_36-0.6_20220914",
      "08-BLCK_T132-2.0_20220915" ~ "08-BLCK_T132-1.8_20220915",
      "09-BRND-2.5_20210728" ~ "09-BRND-1.6_20210728",
      "09-COLE-2.9_20210727" ~ "09-COLE-3.6_20210727",
      "09-COLE-4.6_20210727" ~ "09-COLE-4.2_20210727",
      "12-FOX-1.1_20220809" ~ "12-FOX-1.1_20220810",
      "13-LHUD_T299-2.5_20220720" ~ "13-LHUD_T229-2.5_20220720",
      "13-WFKIL-0.1_20220721" ~ "13-WFKIL-0.4_20220721",
      "16-SUSQ-25.2_20220712" ~ "06-SUSQ-25.2_20220712",
      "10-JACK-0.2_20230726T1030" ~ "10-JKBR-0.2_20230726T1030", # fixing the site that doesn't match - same name as another waterbody 
      .default = event_id
    )
  ) 
}

```


Read in my prepped files and adjust the sample table with Zach's code

```{r}


data_dir<-"L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/processed_bap_scores"

standard_read_csv <- function(file, col_types = NULL) {
  readr::read_csv(
    file = file,
    col_types = col_types,
    na = c("", "NA", "N/A", "n/a", "-9999")
  )
}

import_s_macro_sample <- function(data_dir) {
  standard_read_csv(
    file = file.path(data_dir,
                     "2023_all_2024_deer_river_sample_inf_cleaned_preWQMAval.csv"),
    col_types = cols(
      MSSIH_EVENT_SMAS_HISTORY_ID = col_character(),
      MSSIH_EVENT_SMAS_SAMPLE_DATE = col_date(format = "%Y-%m-%d"), #updated the date format here
      MSSIH_REPLICATE = col_character(),
      MSSIH_TAXONOMIST = col_character(),
      MSSIH_BIOSAMPLE_COLLECT_METHOD = col_character(),
      MSSIH_TOTAL_INDIV_CNT = col_double(),
      MSSIH_GROUP = col_character(),
      EVENT_ID = col_character() #KAR addition since i made these already and we dont have time on the macros
    )
  )
}

prep_s_macro_sample <- function(x, s_event) {
  x |> 
    distinct(
      site_id = MSSIH_EVENT_SMAS_HISTORY_ID,
      sample_date = MSSIH_EVENT_SMAS_SAMPLE_DATE,
      replicate = MSSIH_REPLICATE,
      taxonomist = MSSIH_TAXONOMIST,
      collection_method = MSSIH_BIOSAMPLE_COLLECT_METHOD,
      total_individual_count = MSSIH_TOTAL_INDIV_CNT,
      sample_group = MSSIH_GROUP,
      event_id = EVENT_ID
    ) |> 
    mutate(sample_date = format(sample_date, "%Y%m%d"))|> 
    mutate(sample_group = case_when(
      grepl("[a-zA-Z]", replicate) ~ glue::glue("{sample_group}_{replicate}"),
      .default = sample_group
    ),
    replicate = as.numeric(stringr::str_remove_all(replicate,
                                                   "[a-zA-Z]"))
    ) |> 
    #kar hashed out since we're missing the time
    # tidyr::unite(
    #   "event_id",
    #   site_id,
    #   sample_date
    # ) |> 
    macro_event_corrections() |> 
    correct_site_name(
      vars = "event_id"
     ) 
  #|> 
    # semi_join(s_event,
    #           by = "event_id")
 
  
}

#run the functions
imported_sample<-import_s_macro_sample(data_dir)
prepped_sample_table<-prep_s_macro_sample(imported_sample,s_event = s_event_2023) 

setdiff(prepped_sample_table$event_id, imported_sample$EVENT_ID) 
imported_sample_check<-imported_sample %>% 
  mutate(check = paste(MSSIH_EVENT_SMAS_HISTORY_ID,MSSIH_REPLICATE)) %>% 
  select(check,MSSIH_EVENT_SMAS_HISTORY_ID)

prepped_sample_table_check<-prepped_sample_table %>% 
  mutate(check = paste(site_id,replicate)) %>% 
  select(check)

setdiff(prepped_sample_table_check$check, imported_sample_check$check)

check<-left_join(imported_sample_check, prepped_sample_table_check)



```


Then prep the metrics file using Zach's code

```{r}

import_s_macro_metrics <- function(data_dir) {
  standard_read_csv(
    file = file.path(data_dir,
                     "2023_all_2024_deer_river_metrics_cleaned_preWQMAval.csv"),
           col_types = cols(
             MMDH_RICHNESS = col_double(),
             MMDH_RICHNESS_SCORE = col_double(),
             MMDH_EPT_RICH = col_double(),
             MMDH_EPT_SCORE = col_double(),
             MMDH_HBI_INDEX = col_double(),
             MMDH_HBI_SCORE = col_double(),
             MMDH_SHANNON = col_double(),
             MMDH_SHANNON_SCORE = col_double(),
             MMDH_BIO_ASMT_PROFILE_SCORE = col_double(),
             MMDH_PCT_MODEL_AFFINITY = col_double(),
             MMDH_PCT_MODEL_AFFINITY_SCORE = col_double(),
             MMDH_NUTRIENT_BIOTIC_INDEX_P = col_double(),
             MMDH_NBI_P_SCORE = col_double(),
             MMDH_NCO_RICH = col_double(),
             MMDH_NCO_RICH_SCORE = col_double(),
             MMDH_PCT_DOMINANCE_3 = col_double(),
             MMDH_PCT_DOMINANCE_3_SCORE = col_double(),
             MSSIH_BIOSAMPLE_COLLECT_METHOD = col_character(),
             MSSIH_BIOSAMPLE_COLLECT_METHOD_NUM = col_double(),
             MSSIH_EVENT_SMAS_HISTORY_ID = col_character(),
             MSSIH_EVENT_SMAS_SAMPLE_DATE = col_date(format = "%Y-%m-%d"), #updated by KAR
             MSSIH_REPLICATE = col_double(),
             MSSIH_GROUP = col_character(),
             EVENT_ID = col_character()
           ))
}

prep_s_macro_metrics <- function(x, s_event, s_macro_sample) {
  S_MACRO_METRICS_final <- x |> 
    distinct(
      #kar updates
      site_id = site_id,
      date = MSSIH_EVENT_SMAS_SAMPLE_DATE,
      collection_method = MSSIH_BIOSAMPLE_COLLECT_METHOD,
      replicate = MSSIH_REPLICATE,
      sample_group = MSSIH_GROUP,
      score_bioassessment_profile = MMDH_BIO_ASMT_PROFILE_SCORE,
      raw_richness = MMDH_RICHNESS,
      score_richness = MMDH_RICHNESS_SCORE,
      raw_ept_richness = MMDH_EPT_RICH,
      score_ept_richness = MMDH_EPT_SCORE,
      raw_hilsenhoff_biotic_index = MMDH_HBI_INDEX,
      score_hilsenhoff_biotic_index = MMDH_HBI_SCORE,
      raw_shannon_diversity = MMDH_SHANNON,
      score_shannon_diversity = MMDH_SHANNON_SCORE,
      raw_percent_model_affinity = MMDH_PCT_MODEL_AFFINITY,
      score_percent_model_affinity = MMDH_PCT_MODEL_AFFINITY_SCORE,
      raw_nutrient_biotic_index_phosphorus = MMDH_NUTRIENT_BIOTIC_INDEX_P,
      score_nutrient_biotic_index_phosphorus = MMDH_NBI_P_SCORE,
      raw_non_chiro_oligo_richness = MMDH_NCO_RICH,
      score_non_chiro_oligo_richness = MMDH_NCO_RICH_SCORE,
      event_id = EVENT_ID
     # raw_percent_dominance_3 = MMDH_PCT_DOMINANCE_3,
      #score_percent_dominance_3 = MMDH_PCT_DOMINANCE_3_SCORE # dont have these in the file so i have to hash them out - these are sandy i think?
    ) |> 
    mutate(date = format(date, "%Y%m%d")) |> 
    # tidyr::unite(
    #   "event_id",
    #   site_id,
    #   date
    # ) |> #kar hashed out since i created these already
    mutate(
      collection_method = case_match(
        collection_method,
        "Sediment_Ponar" ~ "Sediment Ponar",
        .default = collection_method
      )
    ) |> 
    macro_event_corrections() |> 
    correct_site_name(
      vars = "event_id"
    ) |> 
    # semi_join(s_event,
    #           by = "event_id") |> #updated by KAR, since we dont have the times
    left_join(
      s_macro_sample,
      by = join_by(event_id, collection_method, replicate, sample_group)
    ) |> 
    select(-taxonomist) |> 
    distinct() |> 
    tidyr::pivot_longer(
      cols = c(score_bioassessment_profile:score_non_chiro_oligo_richness,total_individual_count),
      names_to = "metric_name",
      values_to = "metric_value",
      values_drop_na = TRUE
    ) |> 
    mutate(
      metric_type = case_when(
        grepl("raw", metric_name) ~ "raw",
        grepl("score", metric_name) ~ "score",
        grepl("total_individual_count", metric_name) ~ "raw",
        .default = NA_character_
      ),
      metric_name = stringr::str_remove_all(
        metric_name,
        pattern = "raw_|score_"
      )
    )
  
  S_MACRO_METRICS_standard <- S_MACRO_METRICS_final |> 
    rename(parameter_name = metric_name,
           result_value = metric_value,
           unit = metric_type) |> 
    select(-sample_group) |> 
    mutate(activity_type = "macroinvertebrate_metrics",
           sample_type = "calculated",
           sample_source = "bap_r_package",
           sampling_location = "unknown",
           lab_name = "not_applicable",
           organization_name = "NYSDEC",
           unit = stringr::str_replace_all(unit, "score", "score_0-10"),
           replicate = as.character(replicate),
           parameter_description = assign_s_biosurvey_parameter_description(
             x = parameter_name
           )
    )
  
 
}

assign_s_biosurvey_parameter_description  <- function(x) {
  dplyr::case_match(
    x,
    "bioassessment_profile" ~ "The Biological Assessment Profile (BAP) of index values is a method of plotting individual biological comunity metrics on a common scale of water quality impact. Individual metrics from those described previously are converted to a common 10-scale based on a series of equations. The combination of metrics used differs based on the type of sample collected and the habitat from which the sample was taken. The mean scale value of the indices represents the assessed impact for each site",
    "richness" ~ "This is the total number of species or taxa found in the sample. Higher species richness values are mostly associated with clean-water conditions.",
    "ept_richness" ~ "EPT denotes the total number of species of mayflies (Ephemeroptera), stoneflies (Plecoptera), and caddisflies (Trichoptera) found in a subsample. These are considered to be mostly clean-water organisms in flowing waters, and their presence generally is correlated with good water quality.",
    "hilsenhoff_biotic_index" ~ "The Hilsenhoff Biotic Index is calculated by multiplying the number of individuals of each species by its assigned tolerance value, summing these products, and dividing by the total number of individuals. On a 0-10 scale, tolerance values range from intolerant (0) to tolerant (10). Toleracane values are mostly from Hilsenhoff (1987), but some have been recalibarated based on NYS datasets. High HBI values are indictive of organic (sewage) pollution, while low values indicate lack of sewage effects.",
    "shannon_diversity" ~ "Species diversity is a value that combines species richness and community balance (evenness). Shannon-Wiener diversity values are calculated using the formula in Weber (1973). High species diversity values usually indicate diverse, well-balanced communities, while low values indicate stress or impact.",
    "total_individual_count" ~ "The total number of individuals enumerated. Multiplate samples represent density estimates.",
    "percent_model_affinity" ~ "The Percent Model Affinity for taxonomic group composition is a measure of similarity to a model non-impacted community based on percent abundance in 7 major groups (Novak and Bode, 1992). Percentage similarity as calculated in Washington (1987) is used to measure similarity. Models are descriped in SOP 216.",
    "nutrient_biotic_index_phosphorus" ~ "The Nutrient Biotic Index (Smith et al., 2007) is a diagnostic measure of stream nutrient enrichment identified by macroinvertebrate taxa. The frequency of occurrences of taxa at varying nutrient concentrations allowed the identification of taxon-specific nutrient optima using a method of weighted averaging. The assignment of tolerance values to taxa based on their nutrient optimum provided the ability to reduce macroinvertebrate community data to a linear scale of eutrophication from oligotrophic to eutrophic. Two tolerance values were assigned to each taxon, one for total phosphorus, and one for nitrate. This provides the ability to calculate two different nutrient biotic indices, one for total phosphorus (NBI-P), and one for nitrate (NBI-N). Study of the indices indicate better performance by the NBI-P, with strong correlations to stream nutrient concentrations and diatom communities.",
    "non_chiro_oligo_richness" ~ "Non-Chironomidae and Oligochaeta (NCO) Richness denotes the total number of species of organisms other than those in the groups Chironomidae and Oligochaeta. Since Chironomidae and Oligochaeta are generally the most abundant groups in impacted communities, NCO taxa are considered to be less pollution tolerant, and their presence would be expected to be more indicative of good water quality. This measure is the Sandy Stream counterpart of EPT richness.",
    "percent_dominance_3" ~ "Dominance is a measure of community balance, or evenness of the distribution of individuals among the species. Simple dominance is the percent contribution of the most numerous species. Dominance-3 (rivers and streams) is the combined percent contribution of the three most numerous taxa.",
    .default = NA_character_
  )
}

imported_metrics<-import_s_macro_metrics(data_dir)
prepped_metrics<-prep_s_macro_metrics(imported_metrics, s_event_2023, prepped_sample_table)

#fix the 2 site_id columns by removing one of them
prepped_metrics<-prepped_metrics %>% 
  select(-c(site_id.y)) %>% 
  rename(site_id = site_id.x)

# New names:Warning: The following named parsers don't match the column names: MMDH_PCT_DOMINANCE_3, MMDH_PCT_DOMINANCE_3_SCORE - this is the warning we get, this is because i dont have any metrics that use those columns in this batch.

```

```{r final-checks}
#check to make sure that there are matches

setdiff(prepped_metrics$event_id,prepped_sample_table$event_id)
setdiff(prepped_sample_table$event_id, prepped_metrics$event_id)
#these are good

prepped_metrics %>% skim()
prepped_sample_table %>% skim()

#fix Archer creek AGAIN
prepped_sample_table<-prepped_sample_table %>% 
  mutate(site_id = case_when(event_id %in% "11-ARCH-1.9_20230918T1200" ~ "11-ARCH-1.9",
                             event_id %in% "13-WAPP_E-3.2_20240718T1038" ~ "13-WAPP_E-3.2",
                             event_id %in% "10-JKBR-0.2_20230726T1030" ~ "10-JKBR-0.2",
                             TRUE~site_id))

prepped_metrics<-prepped_metrics %>% 
  mutate(site_id = case_when(event_id %in% "11-ARCH-1.9_20230918T1200" ~ "11-ARCH-1.9",
                             event_id %in% "13-WAPP_E-3.2_20240718T1038" ~ "13-WAPP_E-3.2",
                             event_id %in% "10-JKBR-0.2_20230726T1030" ~ "10-JKBR-0.2",
                             TRUE~site_id))
  

```



```{r}
#check metrics fall within specified range
check<-prepped_metrics %>% 
  filter(parameter_name %in% "bioassessment_profile")
range(check$result_value)  #looks good, should be between 1-10

prepped_metrics2<-prepped_metrics %>% 
  mutate(result_category = case_when(
    parameter_name %in% "bioassessment_profile" & result_value < 2.5 ~ "severly_impacted",
    parameter_name %in% "bioassessment_profile" & between(result_value, 2.5,5.0) ~ "moderately_impacted", 
    parameter_name %in% "bioassessment_profile" & between(result_value, 5.0,7.5) ~ "slightly_impacted", 
    parameter_name %in% "bioassessment_profile" & result_value > 7.5 ~ "non_impacted", 
    TRUE ~ ""
  )) #use event id to determine the flags

#flags for < total amount
event_ids_tc<-prepped_metrics2 %>% 
  filter(parameter_name %in% "total_individual_count") %>% 
  mutate(result_qualifier = case_when(collection_method %in% 
                                 (collection_method %in% "Kick: Standard" & result_value < 100) ~ "<tc",
                                 (collection_method %in% "Kick: Sandy Stream" & result_value < 100) ~ "<tc",
                                 (collection_method %in% "Multiplate: Navigable" & result_value < 250) ~ "<tc",
                                 (collection_method %in% "Multiplate: Non-Navigable" & result_value < 250) ~ "<tc",
                                 (collection_method %in% "Low Gradient" & result_value < 200) ~ "<tc",
                                 (collection_method %in% "Lake Composite" & result_value < 300) ~ "<tc",
                                 TRUE ~ ""
                                 )) %>% 
filter(result_qualifier %in% "<tc" )
#subset the event ids that will need the <tc for the final bap score 
event_ids_tc.l<-unique(event_ids_tc$event_id)

prepped_metrics2<-prepped_metrics2 %>% 
  mutate(result_qualifier = case_when(
    event_id %in% event_ids_tc.l ~ "<tc",
    TRUE ~ ""
  ),
  result_qualifier_description = case_when(
    (event_id %in% event_ids_tc.l & parameter_name %in% "bioassessment_profile")~ "total macroinvertebrate count not met for method in SOP 214, Biological Enumeration",
    TRUE ~ ""
  ))
  
#I was going to update the collection method - but htat looks like it's part of hte sample table, so i will do it here and not in the results table
prepped_sample_table2<-prepped_sample_table %>% 
  mutate(sample_method = case_when(
    collection_method %in% "Kick: Standard" ~ "kick_standard",
    collection_method %in% "Multiplate: Navigable" ~ "multiplate_navigable",
    collection_method %in% "Multiplate: Non-Navigable" ~ "multiplate_non-navigable",
    collection_method %in% "Sediment Ponar" ~ "sediment_ponar",
    collection_method %in% "Kick: Sandy Stream" ~ "kick_sandy-stream",
    collection_method %in% "Kick: Headwater Stream" ~ "kick_standard",
    collection_method %in% "Multihabitat: Lake" ~ "multihabitat_lake",
    collection_method %in% "Low-Gradient" ~ "low_gradient",
    collection_method %in% "Lake: Ponar" ~ "lake_ponar",
    collection_method %in% "Lake: Littoral" ~ "lake_littoral",
    collection_method %in% "Other: Various (Historical)" ~ "ther_various-historical",
   TRUE ~ "unknown"
  ))

#make all column names capital
names(prepped_metrics2) <- base::toupper(names(prepped_metrics2))
names(prepped_sample_table2)<-base::toupper(names(prepped_sample_table2))

```

Write to the staging area

```{r update-flags-and-description}


saveRDS(
  object = prepped_metrics2,
  file = file.path(
    "L:",
    "DOW",
    "BWAM Share",
    "data",
    "data_warehouse_staging",
    "2024_V3",
    "raw_data",
    "bap_metrics.rds"
  )
)

saveRDS(
  object = prepped_sample_table2,
  file = file.path(
    "L:",
    "DOW",
    "BWAM Share",
    "data",
    "data_warehouse_staging",
    "2024_V3",
    "raw_data",
    "bap_sample_table.rds"
  )
)

```

